Argennon: A Scalable Smart Contract Platform

### 2021-06-24 tex/sections/blocks.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Change the structure of chapters
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.5ex]
        \hline\hline
        commitment to the staking database            \\ [1.2ex]
        commitment to the method database             \\ [1.2ex]
        commitment to the heap database               \\ [1.2ex]
        commitment to the set of transactions         \\ [1.2ex]
        last block certificate issued by         \\
        the validators committee                      \\ [1.2ex]
        clustering directives                         \\ [1.2ex]
        random seed                                   \\ [1.2ex]
        previous block hash                           \\ [1.2ex]
        \hline
    \end{tabular}
\end{center}

@@

Given triples $(\PK_i,\ m_i,\ \sigma_i)$ for $i=1,\ldots,n$,
anyone can aggregate the signatures $\sigma_1,\ldots,\sigma_n \in \G_0$
into a short convincing aggregate signature $\sigma$ by computing
\begin{equation}
    \label{eq:agg}
    \sigma \gets \sigma_1 \cdots \sigma_n \in \G_0.
\end{equation}
Verifying an aggregate signature $\sigma \in \G_0$ is done by checking that
\begin{equation}
    \label{eq:aggdiff}
    e(g_1, \sigma) = e\big(\PK_1,\ \Hm(m_1)\big) \cdots e\big(\PK_n,\ \Hm(m_n)\big).
\end{equation}
When all the messages are the same ($m = m_1 = \ldots = m_n$), the verification relation~\eqref{eq:aggdiff} reduces to
a simpler test that requires only two pairings:
\begin{equation}
    \label{eq:aggsame}
    e(g_1, \sigma) = e\Big(\PK_1 \cdots \PK_n,\ \Hm(m)\Big).
\end{equation}
We call $\APK=\PK_1 \cdots \PK_n$ the aggregate public key.

@@

Argennon block certificates constitute an ordered sequence based on the order of blocks they certify. If we show
the certificate of committee $C$ for the $i$-th block\footnote{note that the $i$-th block certificate is not
necessarily the certificate of the $i$-th block.} with $\C_i$, and the set of signers
with $S_i$, then the block certificate $\C_i$ can be considered as a tuple:
\begin{equation}
    \C_i=(\sigma_i,\ C-S_{i})\label{eq:cert},
\end{equation}
where $\sigma_i$ is the aggregate signature issued by $S_i$.

>>>>

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.5ex]
        \hline\hline
        commitment to the staking database            \\ [1.2ex]
        commitment to the method database             \\ [1.2ex]
        commitment to the heap database               \\ [1.2ex]
        commitment to the set of transactions         \\ [1.2ex]
        a consecutive list of block certificates issued     \\
        by validators' committee (if any)           \\ [1.2ex]
        clustering directives                         \\ [1.2ex]
        random seed                                   \\ [1.2ex]
        previous block hash                           \\ [1.2ex]
        \hline
    \end{tabular}
\end{center}

@@

Given triples $(\PK_i,\ m_i,\ \sigma_i)$ for $i=1,\ldots,n$,
anyone can aggregate the signatures $\sigma_1,\ldots,\sigma_n \in \G_0$
into a short convincing aggregate signature $\sigma$ by computing
\begin{equation}
    \label{eq:agg}
    \sigma \gets \sigma_1 \cdots \sigma_n \in \G_0\ .
\end{equation}
Verifying an aggregate signature $\sigma \in \G_0$ is done by checking that
\begin{equation}
    \label{eq:aggdiff}
    e(g_1, \sigma) = e\big(\PK_1,\ \Hm(m_1)\big) \cdots e\big(\PK_n,\ \Hm(m_n)\big)\ .
\end{equation}
When all the messages are the same ($m = m_1 = \ldots = m_n$), the verification relation~\eqref{eq:aggdiff} reduces to
a simpler test that requires only two pairings:
\begin{equation}
    \label{eq:aggsame}
    e(g_1, \sigma) = e\Big(\PK_1 \cdots \PK_n,\ \Hm(m)\Big)\ .
\end{equation}
We call $\APK=\PK_1 \cdots \PK_n$ the aggregate public key.

@@

Argennon block certificates constitute an ordered sequence based on the order of blocks they certify. If we show
the certificate of committee $C$ for the $i$-th block\footnote{note that the $i$-th block certificate is not
necessarily the certificate of the $i$-th block.} with $\C_i$, and the set of signers
with $S_i$, then the block certificate $\C_i$ can be considered as a tuple:
\begin{equation}
    \C_i=(\sigma_i,\ C-S_{i})\label{eq:cert}\ ,
\end{equation}
where $\sigma_i$ is the aggregate signature issued by $S_i$.

### 2021-06-24 tex/sections/consensus.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon protocol calculates a stake value for every account, which is an estimate of a user's stake in the
system. This value is measured in ARGs. Every $n$ block randomly $m$ committees are selected from
accounts whose stake value is higher than \texttt{minValidatorsStake} threshold. This
threshold is determined by the ADAGs, but it can never be higher than $100$ ARGs.
These committees are chosen in a
way that the total stake of members of each committee is approximately equal and every account is a member of at
least one committee.

Every member of a validators committee has a status which can be either \texttt{online} or \texttt{offline}.
This status is stored in the ARG smart contract, and it can be changed through a method invocation
from this smart contract. When an account sets its status to \texttt{offline}, it receives a small reward, and
it can not change it back to \texttt{online} for \texttt{statusCoolDown} number of blocks.

\note{When an account changes its status, the change has no effect until the block containing the status
change transaction gets certified by the committee of validators.}

A block certificate issued by some members of a validators committee is considered valid, if according to
the staking database of the previous \textbf{block certified by the same committee}, we have:
\begin{itemize}
    \item The total stake of \texttt{online} members is higher than \texttt{minOnlineStake} percent of the
    total stake of all members. This threshold can be changed by the ADAGs, but it can never be lower
    than 70 percent.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than 80 percent of the total stake
    of committee members that have \texttt{online} status.
\end{itemize}

@@

As we mentioned before, every $m$ blocks of the Argennon blockchain needs a certificate from a specific committee
of validators. To decide about signing the block certificate, an honest member of the validators'
committee checks the conditional validity of the committee block, and if the block is valid he issues an "accept"
signature, otherwise he issues a "reject" signature.

@@

In Argennon, signature aggregation is mostly performed by ZK-EDB servers. To distribute the aggregation workload
between different servers, The committee of validators is divided into pre-determined groups, and each ZK-EDB
server is responsible for signature aggregation of one group. To make sure that there is enough redundancy, the number
of groups should be less than the number of ZK-EDB servers and each group should be assigned to
multiple ZK-EDB servers.

>>>>

The Argennon protocol calculates a stake value for every account, which is an estimate of a user's stake in the
system. This value is measured in ARGs. Every $n$ block randomly $m$ committees are selected from
accounts whose stake value is higher than \texttt{minValidatorsStake} threshold. This
threshold is determined by the ADAGs, but it can never be higher than $100$ ARGs.
These committees are chosen in a
way that the total stake of members of each committee is approximately equal and every account is a member of
\textbf{at least} one committee.

Every member of a validators' committee has a status which can be either \texttt{online} or \texttt{offline}.
This status is stored in the ARG smart contract and is a part of the staking database. A validator can change
his status through a method invocation
from this smart contract. When an account sets its status to \texttt{offline}, it receives a small reward, and
it can not change it back to \texttt{online} for \texttt{statusCoolDown} number of blocks.

\note{When a validator changes his status, the change has no effect until the block containing the status
change transaction gets certified by his committee.}

A block certificate issued by some members of a validators' committee is considered valid, if according to
the staking database of the previous block \textbf{certified by the same committee}, we have:
\begin{itemize}
    \item The total stake of \texttt{online} members is higher than \texttt{minOnlineStake} percent of the
    total stake of all members. This threshold can be changed by the ADAGs, but it can never be lower
    than 70 percent.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than 80 percent of the total stake
    of committee members that have \texttt{online} status.
\end{itemize}

@@

As we mentioned before, every block of the Argennon blockchain needs a certificate from a specific committee of
validators, which repeats every $m$ blocks. To decide about signing the block certificate, an honest member of a
validators' committee checks the conditional validity of the committee block, and if the block is valid he issues
an "accept" signature, otherwise he issues a "reject" signature.

block certificates issued by validators' committees are included in the Argennon blockchain. A block may contain
multiple certificates, provided that those certificates belong to consecutive blocks.

@@

In Argennon, signature aggregation is mostly performed by ZK-EDB servers. To distribute the aggregation workload
between different servers, Every committee of validators is divided into pre-determined groups, and each ZK-EDB
server is responsible for signature aggregation of one group. To make sure that there is enough redundancy, the
total number of groups should be less than the number of ZK-EDB servers and each group should be assigned to
multiple ZK-EDB servers.
